Viscous Transport in Eroding Porous Media

### 2019-08-05 docs/transport/erosion_transport.tex
editing the tex of fig.8 in transport paper
small change of caption of fig. 13 in transport paper

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/anomalous_diffusion20d_new}
%\caption{\label{fig:Eroding20anomalous} The
%mean squared displacement of the tracer trajectories  at several
%different stages of the erosion process.  As the porosity increases, the
%mean squared displacement tends towards $\sigma^2_\lambda(t) \sim t^$
%}
\includegraphics*[width =0.45\linewidth]{./figs/20b_first_moment}
\includegraphics*[width =0.45\linewidth]{./figs/20b_second_moment}
\caption{\label{fig:Eroding20anomalous} The analysis of anomalous diffusion in
 20 nearly touching bodies with respect to six porosities and the reference line of 100\% porosity.
The first moment (left) is the mean length of streamlines and the second moment (right) is the }
\end{figure}

@@

\begin{figure}[H]
\center
\includegraphics*[width =0.45\linewidth]{./figs/100b_first_moment}
\includegraphics*[width =0.45\linewidth]{./figs/100b_second_moment}
\caption{\label{fig:Eroding100anomalous} The analysis of anomalous diffusion in
 100 bodies with respect to six porosities and the reference line of 100\% porosity.
The first moment (left) is the mean length of streamlines and the second moment (right) is the }
\end{figure}

>>>>

\begin{figure}[H]
%\caption{\label{fig:Eroding20anomalous} The
%mean squared displacement of the tracer trajectories  at several
%different stages of the erosion process.  As the porosity increases, the
%mean squared displacement tends towards $\sigma^2_\lambda(t) \sim t^$
%}
\includegraphics*[width =0.45\linewidth]{./figs/20b_first_moment}
\includegraphics*[width =0.45\linewidth]{./figs/20b_second_moment}
\caption{\label{fig:Eroding20anomalous} The analysis of anomalous diffusion in
 20 nearly touching bodies with respect to six porosities and the reference line of 100\% porosity.
The first moment (left) is the mean length of streamlines and the second moment (right) is the }
\end{figure}

@@

\begin{figure}[H]
\center
\includegraphics*[width =0.45\linewidth]{./figs/100b_first_moment}
\includegraphics*[width =0.45\linewidth]{./figs/100b_second_moment}
\caption{\label{fig:Eroding100anomalous} The analysis of anomalous diffusion in
 100 bodies with respect to five porosities and the reference line of 100\% porosity.
The first moment (left) is the mean length of streamlines and the second moment (right) is the }
\end{figure}
